Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction

### 2024-02-19 paper/paper.tex
updated with latest version of the text

\acknowledgments{Don MacLaughlin, Scotty MacLaughlin and the City of Plano, TX, are gratefully acknowledged for allowing us to deploy the autonomous robot team on their property. Dr. Christopher Simmons is gratefully acknowledged for his computational support. We thank Dr. Antonio Mannino for his advice in selecting the robotic boat sensing suite. Annette Rogers is gratefully acknowledged for support in arranging insurance coverage. Steven Lyles is gratefully acknowledged for support in arranging a secure place for the robot team. The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research, the NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.}

>>>>

\acknowledgments{Don MacLaughlin, Scotty MacLaughlin and the City of Plano, TX, are gratefully acknowledged for allowing us to deploy the autonomous robot team on their property. Dr. Christopher Simmons is gratefully acknowledged for his computational support. We thank Dr. Antonio Mannino for his advice in selecting the robotic boat sensing suite. Annette Rogers is gratefully acknowledged for support in arranging insurance coverage. Steven Lyles is gratefully acknowledged for support in arranging a secure place for the robot team. The authors acknowledge the OIT-Cyberinfrastructure Research Computing group at the University of Texas at Dallas and the TRECIS CC* Cyberteam (NSF #2019135) for providing HPC resources that contributed to this research, NSF OAC-2115094 Award, and EPA P3 grant number 84057001-0.}
